Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-16 analysis/memo2_TAS_reviewers.Rmd
minor edits

We have revised the paper in paragraph 2 to expressly distinguish between "bias" as the illegal strike bias (the parameter to be estimated) from "bias" in the statistical sense.  We hope this reduces any confusion.

@@

_(page 10, lines 25-29) Does the application allow users to revise the historical data used? That is, should there be guidance about choosing between low α with all the historical data or large α with a subset of the historical data? That is, it seems your approach can be compatible with the stratified approach of Gastwirth and Xu (2014) – would that improve the issue with heterogeneous historical data?_

>>>>

We have revised the paper in paragraph 2 to expressly distinguish between "bias" as the illegal strike bias (the parameter to be estimated) from "bias" in the statistical sense.  We hope this reduces any confusion.[EDITME]

@@

_(page 10, lines 25-29) Does the application allow users to revise the historical data used? That is, should there be guidance about choosing between low $\alpha$ with all the historical data or large α with a subset of the historical data? That is, it seems your approach can be compatible with the stratified approach of Gastwirth and Xu (2014) – would that improve the issue with heterogeneous historical data?_

### 2023-06-16 analysis/paper_draft4.Rmd
minor edits

Since _Batson v. Kentucky_ [-@batson1986], a party violates the Equal Protection Clause of the United States Constitution by using peremptory challenges if motivated by the prospective jurors' race, ethnicity, sex, or membershhip in another category that the law prohibits as a basis for striking that juror. The party bringing a _Batson_ challenge bears the burden of proving such illegal bias is more likely than not to be true [@LaFave2022, $\S$ 22.3(d)]. Such illegal strike bias is the parameter of interest, not to be confused with "bias" in a statistical sense, or bias in a parameter [EDITME].

>>>>

Since _Batson v. Kentucky_ [-@batson1986], a party violates the Equal Protection Clause of the United States Constitution by using peremptory challenges if motivated by the prospective jurors' race, ethnicity, sex, or membership in another category that the law prohibits as a basis for striking that juror. The party bringing a _Batson_ challenge bears the burden of proving such illegal bias is more likely than not to be true [@LaFave2022, $\S$ 22.3(d)]. Such illegal strike bias is the parameter of interest, not to be confused with "bias" in a statistical sense, or bias in a parameter [EDITME].
